---
title: "HAB-DW-Risk-Viewer-NEWS"
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# HAB-DW-Risk-Viewer 0.3 (2025-08-20)

* refactor: Bump version number for deliverable

# HAB-DW-Risk-Viewer 0.2.0.9004 (2025-08-20)

* refactor: Make summary figures and table reactive

# HAB-DW-Risk-Viewer 0.2.0.9003 (2025-08-20)

* refactor: Update spinner for leaflet (no longer needed)
* refactor: Update tooltips to bsplus package
* refactor: Add legend to map
* refactor: Add dummy file to results folder
    + Avoids an empty directory for when load to Shiny server

# HAB-DW-Risk-Viewer 0.2.0.9002 (2025-08-15)

* refactor: Add download button for summary and results

# HAB-DW-Risk-Viewer 0.2.0.9001 (2025-08-15)

* refactor: Modify map
    + Remove color outline for points
    + Filter points and polygons to remove those with NA values
* refactor: Update summary tab
    + Ensure table shows up
    + Add text above each element to describe the element

# HAB-DW-Risk-Viewer 0.2 (2025-08-15)

* refactor: Bump version number for deliverable

# HAB-DW-Risk-Viewer 0.1.0.9011 (2025-08-14)

* refactor: Update HUC layer pop up
    + Add waterbody and model

# HAB-DW-Risk-Viewer 0.1.0.9010 (2025-08-14)

* refactor: Updates maps
    + Move HUCS (points and polygons) to top to allow mouseover
    + Add control groups

# HAB-DW-Risk-Viewer 0.1.0.9009 (2025-08-14)

* refactor: Updates to Summary tab

# HAB-DW-Risk-Viewer 0.1.0.9009 (2025-08-13)

* refactor: Move states boundary file to RDS
* refactor: Create data-raw file to create states boundary
* refactor: Move 'map' tab to front so activates and always works
* refactor: Crop to state boundaries not bounding box

# HAB-DW-Risk-Viewer 0.1.0.9008 (2025-08-11)

* feature: Add summary plots and tables
    + placeholders only
* refactor: Add tigiris cache
* docs: Add missing packages from imported summary code

# HAB-DW-Risk-Viewer 0.1.0.9007 (2025-08-11)

* refactor: Add USEPA template for web
* refactor: Remove 'crop' button, leave in code
* docs: Add packages to DESCRIPTION

# HAB-DW-Risk-Viewer 0.1.0.9006 (2025-08-08)

* refactor: Use points and not polygons
* refactor: Update text on some tabs

# HAB-DW-Risk-Viewer 0.1.0.9005 (2025-06-13)

* nearly finished version, still have work to do

# HAB-DW-Risk-Viewer 0.1.0.9004 (2024-11-05)

* refactor: Finish setting up files as a proper repo, Issue #1
* refactor: Set up dummy Shiny app (Old Faithful)
* refactor: Modify Shiny to use USEPA template, Issue #2
    + Separate files for header, footer, css, tags
    + Use files from ContDataQC Shiny app

# HAB-DW-Risk-Viewer 0.1.0.9003 (2024-11-04)

* refactor: Add issue templates via web

# HAB-DW-Risk-Viewer 0.1.0.9002 (2024-11-04)

* docs: Update license in DESCRIPTION

# HAB-DW-Risk-Viewer 0.1.0.9001 (2024-11-04)

* refactor: Initial commit setting up package and shiny app